Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-22 papers/pair-correlation/paper.tex
Completed derivation of chi_T in paper.

We construct $g(r, g_\sigma)$ using several constraints.  Naturally,
\begin{equation}
  g(\sigma, g_\sigma) = g_\sigma.
\end{equation}
In addition, we know that
\begin{equation}
  \begin{split}
    1 + n\int\left[g(r)-1\right]d\rr = nkT\chi_T\\
    \chi_T  = -\frac{1}{V}\left(\frac{\partial V}{\partial p}\right)_T
    = - \left(V\left(\frac{\partial p}{\partial V}\right)_T\right)^{-1}\\
    p = \frac{1+\eta+\eta^2-\eta^3}{(1-\eta)^3}\Longrightarrow \left(\frac{\partial p}{\partial V}\right)_T = \frac{dp}{d\eta}\frac{d\eta}{dV}\\
    \eta = \frac{4\pi R^3N}{3V}\Longrightarrow \frac{d\eta}{dV} = -\frac{\eta}{V}\\
    \left(\frac{\partial p}{\partial V}\right)_T = -\frac{\eta}{V}\left[\frac{1 + 2\eta - 3\eta^2}{(1-\eta)^3} + 3\frac{1 + \eta + \eta^2 - \eta^3}{(1-\eta)^4}\right]\\
  %\int (g(r)-1)d\rr &= \frac{\chi_T}{kT} \\
  %&= \eta \eta \cdots \fixme{fill in, double-check}
  \end{split}
\end{equation}
where $\chi_T$ is the isothermal compressibility, for which we use the
Carnahan-Starling equation of state.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted lin on the plot to the
    left.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted lin on the plot to the
    left.}\label{fig:triplet-distribution-4}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    separated by the diameter of one sphere.}\label{fig:triplet-gap-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    separated by the diameter of one sphere.}\label{fig:triplet-gap-distribution-4}
\end{figure}

@@

    + \frac{1}{2}\mathop{\mathop{\sum_{i<j}}_{k<l}}_{kl \ne ij}

@@

  + \frac{1}{2}\mathop{\mathop{\sum_{k<l}}_{m<n}}_{kl\ne mn}

@@

  \frac{N^2}{2}\iiiint \Theta(\sigma+\delta-r_{12})

@@

  - \frac{N^4}{8}\iiiint

@@

  \shoveleft{\quad= \frac{nN}{2} \int_{\sigma}^{\sigma+\delta} g(r) d\rr }
  - \frac{n^2N^2}{8} \left(\int_{\sigma}^{\sigma+\delta} g(r)

@@

  + \cdots

>>>>

We construct $g(r, g_\sigma)$ using several constraints.  Naturally,
\begin{equation}
  g(\sigma, g_\sigma) = g_\sigma.
\end{equation}
In addition, we know that
\begin{align}
  1 + n\int\left[g(r)-1\right]d\rr &= nkT\chi_T
\end{align}
\begin{equation}
  \begin{split}
    \chi_T  &= -\frac{1}{V}\left(\frac{\partial V}{\partial p}\right)_T
    = - \left(V\left(\frac{\partial p}{\partial V}\right)_T\right)^{-1}\\
    p &= nkT\frac{1+\eta+\eta^2-\eta^3}{(1-\eta)^3}\\
    \left(\frac{\partial p}{\partial V}\right)_T &= \frac{\partial p}{\partial\eta}\frac{\partial\eta}{\partial V} + \frac{\partial p}{\partial n}\frac{\partial n}{\partial V}\\
    n &= \frac{N}{V}\Longrightarrow \frac{\partial n}{\partial V} = -\frac{N}{V^2} = -\frac{n}{V}\\
    \eta &= \frac{4\pi R^3N}{3V}\Longrightarrow \frac{d\eta}{dV} = -\frac{\eta}{V}\\
    \left(\frac{\partial p}{\partial V}\right)_T &= -nkT\frac{\eta}{V}\left[\frac{1 + 2\eta - 3\eta^2}{(1-\eta)^3} + 3\frac{1 + \eta + \eta^2 - \eta^3}{(1-\eta)^4}\right]\\
    &  - \frac{nkT}{V}\left[\frac{1+\eta+\eta^2-\eta^3}{(1-\eta)^3}\right]\\
    &= -nkT\frac{\eta}{V}\left[\frac{(1+2\eta-3\eta^2)(1-\eta) + 3 + 3\eta + 3\eta^2 - 3\eta^3}{(1-\eta)^4}\right]\\
    &  - \frac{nkT}{V}\left[\frac{(1+\eta+\eta^2-\eta^3)(1-\eta)}{(1-\eta)^4}\right]\\
    &= -\frac{kT}{V}\left[\frac{4\eta + 4\eta^2 - 2\eta^3}{(1-\eta)^4} + \frac{1 - 2\eta^3 + \eta^4}{(1-\eta)^4}\right]\\
    nkT\chi_T &= \frac{(1-\eta)^4}{1 + 4\eta + 4\eta^2 - 4\eta^3 + \eta^4}
  %\int (g(r)-1)d\rr &= \frac{\chi_T}{kT} \\
  %&= \eta \eta \cdots \fixme{fill in, double-check}
  \end{split}
\end{equation}
where $\chi_T$ is the isothermal compressibility, for which we use the
Carnahan-Starling equation of state.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    in contact.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-contact-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    in contact.}\label{fig:triplet-distribution-4}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    separated by the diameter of one sphere.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-pretty-inbetween-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    separated by the diameter of one sphere.}\label{fig:triplet-distribution-4}
\end{figure}

@@

    + \mathop{\mathop{\sum_{i<j}}_{k<}}_{kl \ne ij}

@@

  + \mathop{\mathop{\sum_{k<l}}_{m<n}}_{kl\ne mn}

@@

  N^2\iiiint \Theta(\sigma+\delta-r_{12})

@@

  - \frac{N^3}{2}\iiiint

@@

  \shoveleft{\quad= nN \int_{\sigma}^{\sigma+\delta} g(r) d\rr }
  - \frac{n^2N}{2} \left(\int_{\sigma}^{\sigma+\delta} g(r)

@@

  + \frac{n^3N}{6} \left(\int_{\sigma}^{\sigma+\delta} g(r)
  d\rr\right)^3 + \cdots
